Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-13 vesicle_code/docs/adhesion/adhesion.tex
appendix B

To characterize the rheological properties of the suspension of a
doublet, it is necessary to compute the shear and normal stresses.  At a
point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the  pressure
$p(\xx)$ and total stress tensor $T = - p I + \nabla \uu + \nabla \uu^T$
of the single-layer potential~\eqref{eqn:SLP} are
\begin{align*}
    p(\xx) &= \frac{1}{2\pi} \int_{\gamma} 
    \frac{(\xx - \yy) \cdot \xxi}{\|\xx-\yy\|^2} ds_\yy, \\
    T(\xx) &= -\frac{1}{\pi}\int_{\gamma}
      \frac{(\xx-\yy) \cdot \xxi}{\|\xx - \yy\|^2} 
      \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} ds_\yy.
\end{align*}
To compute the stress tensor on a vesicle, there is a jump in the layer
potential, and the stress tensor is
\begin{align*}
  T(\xx) = \frac{1}{2}(\nn \otimes \xxi) + \frac{1}{2} \left(
    \tt \otimes \left[
    \begin{array}{cc}
      2 t_x t_y & t_y^2 - t_x^2 \\
      t_y^2 - t_x^2 & -2 t_x t_y
    \end{array}
    \right] \xxi \right) + 
  \SS_T[\xxi](\xx), \quad \xx \in \gamma,
\end{align*}
where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
vector, respectively.  With the stress tensor computed for $\xx \in
\gamma$, the shear and normal stresses are
\begin{align*}
  \tau^\tt = (T \nn) \cdot \tt, \qquad
  \tau^\nn = (T \nn) \cdot \nn.
\end{align*}

>>>>

To characterize the rheological properties of the suspension of a
doublet, it is necessary to compute the shear and normal stresses.  At a
point $\xx \in \RR^2 \backslash \gamma$ in the fluid bulk, the  pressure
$p(\xx)$ and total stress tensor $T = - p I + \nabla \uu + \nabla \uu^T$
of the single-layer potential~\eqref{eqn:SLP} are
\begin{align*}
    p(\xx) &= \frac{1}{2\pi} \int_{\gamma} 
    \frac{(\xx - \yy) \cdot \xxi}{\|\xx-\yy\|^2} ds_\yy, \\
    T(\xx) &= -\frac{1}{\pi}\int_{\gamma}
      \frac{(\xx-\yy) \cdot \xxi}{\|\xx - \yy\|^2} 
      \frac{(\xx - \yy) \otimes (\xx - \yy)}{\|\xx - \yy\|^2} ds_\yy.
\end{align*}
From these identities and the jump in the stress tensor, we compute the
traction vector on the vesicle as
\begin{align*}
  T\nn = \left(T(\xx) + 
  \frac{1}{2}(\nn \otimes \xxi) + \frac{1}{2} 
    \tt \otimes \left[
    \begin{array}{cc}
      2 t_x t_y & t_y^2 - t_x^2 \\
      t_y^2 - t_x^2 & -2 t_x t_y
    \end{array}
    \right] \xxi\right) \nn, \quad \xx \in \gamma,
\end{align*}
where $\nn$ and $\tt$ are the vesicle's outward unit normal and tangent
vector, respectively.

%With the stress tensor computed for $\xx \in
%\gamma$, the shear and normal stresses are
%\begin{align*}
%  \tau^\tt = (T \nn) \cdot \tt, \qquad
%  \tau^\nn = (T \nn) \cdot \nn.
%\end{align*}
